NeuroElectro: A Window to the World's Neuron Electrophysiology Data

### 2014-03-18 neuroelectro_frontiers/main.tex
minor spacing changes

However, more widespread inclusion of fundamental electrophysiological measurements in data tables in future publications will strongly facilitate data-sharing and meta-analysis initiatives such as NeuroElectro.  
We believe that, if successful, the use of NeuroElectro will influence the practices of scientists writing papers and reporting results.  
Specifically, we recommend the usage of common standards and definitions for basic physiological measurements\citep{toledo-rodriguez_correlation_2004} and neuron types\citep{ascoli_petilla_2008,larson_neurolex.org:_2013}.  
Moreover, we advocate that, where possible, scientists report more basic physiological data overall and report such data using machine-parsable data tables.  
These recommendations could be made informally by journals (in particular, requested by reviewers during manuscript review) as well as by funding agencies.
This change would make it easier for scientists to find and make use of data collected by others.  
Such a culture shift has the potential to make science function more effectively and efficiently to facilitate discovery.

>>>>

However, more widespread inclusion of fundamental electrophysiological measurements in data tables in future publications will strongly facilitate data-sharing and meta-analysis initiatives such as NeuroElectro.  
We believe that, if successful, the use of NeuroElectro will influence the practices of scientists writing papers and reporting results.  
Specifically, we recommend the usage of common standards and definitions for basic physiological measurements \citep{toledo-rodriguez_correlation_2004} and neuron types \citep{ascoli_petilla_2008,larson_neurolex.org:_2013}.  
Moreover, we advocate that, where possible, scientists report more basic physiological data overall and report such data using machine-parsable data tables.  
These recommendations could be made informally by journals (in particular, requested by reviewers during manuscript review) as well as by funding agencies.
This change would make it easier for scientists to find and make use of data collected by others.  
Such a culture shift has the potential to make science function more effectively and efficiently to facilitate discovery.
